% !TEX TS-program = xelatex
% !TEX encoding = UTF-8
% !TEX spellcheck = en-GB

\documentclass[]{friggeri-cv}

\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{calc}
\usepackage{xifthen}
\usepackage[heightr=0.4,roundnessr=0,subdivisions=1,borderwidth=0pt,width=1cm]{progressbar}

\usetikzlibrary{calc}

\patchcmd{\aside}
{\begin{textblock}{3.6}(1.5, 4.33)}
    {\begin{textblock}{5.3}(0, 4.33)}
        {}{}

\begin{document}
\header{Baptiste }{Candellier}
{junior Android developer}

% In the aside, each new line forces a line break
\begin{aside}
    \section{profile}
    French nationality
    25 years old
    Based in Lyon, France
    ~
    \href{tel:0033641666355}{+33 6 41 66 63 55}
    \href{mailto:baptiste.candellier@gmail.com}{baptiste.candellier@gmail.com}
    \href{https://baptiste.candellier.me}{baptiste.candellier.me}
    \href{https://www.linkedin.com/in/candellierba/}{linkedin.com/in/candellierba}
    \section{languages}
    native French
    fluent English
    basic Spanish
    \section{programming}
    Kotlin (Android; Multiplatform)
    Java (Android; server-side)
    ~
    \textit{References available}
    \textit{on request.}
\end{aside}

\section{experience}

\begin{entrylist}
    \entry
    {jan. 2018--today}
    {\href{https://www.tapptic.com}{Tapptic} \textnormal{for} \href{https://www.bedrockstreaming.com}{Bedrock} (previously M6 Web)}
    {Lyon}
    {Maintenance and developpement of Android AVOD apps: \emph{6play (France)}, \emph{RTLplay (Belgium)}, \emph{RTL Most (Hungary)}, \emph{RTLplay (Croatia)}. \\Expansion of the platform with a major rebuild to develop \emph{Salto}'s SVOD app and future clients'.}
    {Android, Kotlin, Java, RxJava, Toothpick, Retrofit, Picasso, Bitrise, diverse analytics platforms, Terraform + AWS}

    \entry
    {sep. 2018--dec. 2018}
    {\href{https://www.keyconsulting.fr}{Key Consulting} \textnormal{for} \href{https://www.natixis.com}{Natixis}}
    {Caen}
    {Continuation of my work on Natixis's billing software project.}{}

    \entry
    {sep. 2015--aug. 2018}
    {\href{https://www.natixis.com}{Natixis} \textnormal{(Apprenticeship)}}
    {Caen}
    {3-year apprenticeship with ENSICAEN. \csharp .NET and Java development in an agile team dedicated to the creation of internally-used software. 3-month mission in the Porto branch.}
    {Telerik, API .NET Core, UX design, LDAP, IBM FileNet, TDD/BDD, Spring}

    \entry
    {apr.--june\\2015}
    {\href{https://www.nxp.com}{NXP Semiconductors} \textnormal{(Internship)}}
    {Colombelles}
    {Development of a Java EE module that integrates an application into an Active Directory server, in a small agile team.}
    {LDAP, Java EE, kanban, Apache Tomcat, Inkscape}
\end{entrylist}

\section{education}

\begin{entrylist}
    \entry
    {2015--2018}
    {Engineer's degree {\normalfont in software engineering}}
    {ENSICAEN, Caen}
    {Specialisation in electronic transactions \& security. 3-yr apprenticeship.}{}

    \entry
    {2013--2015}
    {Higher National Degree {\normalfont in software development}}
    {Université de Caen}
    {Databases, C, Java, PHP, economy, communication...}{}

    \entry
    {2013}
    {A-Levels}
    {Lycée Charles de Gaulle, Caen}
    {Scientific \textit{baccalauréat} in mathematics, physics, chemistry, biology.}{}
\end{entrylist}

\section{projects}

\begin{entrylist}
    \entry
    {2020--ajd.}
    {Home Slide for Home Assistant}
    {\href{https://github.com/outadoc/home-slide-android}{github.com/outadoc/home-slide-android}}
    {Free and open-source Android app that allows controlling Internet of Things software (Home Asssitant).}
    {Kotlin, coroutines, view models, Koin, Wear OS, flow OAuth2}

    \entry
    {2020}
    {CHIP-8 interpretor}
    {\href{https://github.com/outadoc/kemu-chip8}{github.com/outadoc/kemu-chip8}}
    {Kotlin/Multiplatform playground project. A CHIP-8 interpretor/emulator that allows loading programs, written in pure Kotlin, with Java and JS clients.}
    {Kotlin, coroutines, Kotlin/Multiplatform}

\end{entrylist}

\end{document}
